Embedding Intuitionistic into Classical Logic

### 2022-07-15 CSL/lipics-v2021-EIICL.tex
typos

\begin{definition}
\label{def:fo-fulfilled}
	Suppose we are given a counter-model $\mathcal M = (M, I)$ for $\varphi^\circ$. For $\psi = \forall\vec z\psi'\in\mathcal F_\to$ we say it is \textit{fulfilled} at $u\in M$ with $\vec m\in M^n$ iff $(A_\psi^I(\vec a, u)\to B_\psi^I(\vec b, u))[\vec m/\vec z]$ is false or $C_\psi^I(\vec c, u)[\vec m/\vec z]$ is true.
	For $\psi = \forall\vec z\psi'\in\mathcal F_\forall$ we say it is \textit{fulfilled} at $u\in M$ with $\vec m\in M^n$ iff there is $m\in M$ with $E^{I}(m, u)$ such that $A^{I[m/x]}_\psi(\vec a)[\vec m/\vec z]$ is false or $B_\psi^I(\vec b)[\vec m/\vec z]$ is true.
\end{definition}

>>>>

\begin{definition}
\label{def:fo-fulfilled}
	Suppose we are given a counter-model $\mathcal M = (M, I)$ for $\varphi^\circ$. For $\psi = \forall\vec z\psi'\in\mathcal F_\to$ we say it is \emph{fulfilled} at $u\in M$ with $\vec m\in M^n$ iff $(A_\psi^I(\vec a, u)\to B_\psi^I(\vec b, u))[\vec m/\vec z]$ is false or $C_\psi^I(\vec c, u)[\vec m/\vec z]$ is true.
	For $\psi = \forall\vec z\psi'\in\mathcal F_\forall$ we say it is \emph{fulfilled} at $u\in M$ with $\vec m\in M^n$ iff there is $m\in M$ with $E^{I}(m, u)$ such that $A^{I[m/x]}_\psi(\vec a)[\vec m/\vec z]$ is false or $B_\psi^I(\vec b)[\vec m/\vec z]$ is true.
\end{definition}
